Practical implications of HATEOAS on a bridge between LOD and SPARQL

### 2012-02-27 eswc-2012/workshop.tex
lowercase
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@117 43ef1190-90fd-4dd7-a769-d0121f02b80e

Semantic Web services is likely to be an important source of data for
future applications, but for foreseeable future just one of many. A
key promise of Linked Open Data (LOD) in particular, and the Semantic
Web in general is the ability to integrate many data sources
easily. However, this integration requires links and it requires that
the resulting graph can be traversed by reasonable means. While links
are quite abundant across the LOD cloud, this paper will argue that
key links are missing to make it possible to traverse the resulting
graph. Moreover, we will argue that this shortcoming is due to that
the community does not adequately take into account the constraint
known as ``Hypermedia As The Engine Of Application State'' (commonly
abbreviated HATEOAS) from the REST architectural style, see
\cite{fielding}~Chapter~5.

>>>>

Semantic Web services is likely to be an important source of data for
future applications, but for foreseeable future just one of many. A
key promise of Linked Open Data (LOD) in particular, and the Semantic
Web in general is the ability to integrate many data sources
easily. However, this integration requires links and it requires that
the resulting graph can be traversed by reasonable means. While links
are quite abundant across the LOD cloud, this paper will argue that
key links are missing to make it possible to traverse the resulting
graph. Moreover, we will argue that this shortcoming is due to that
the community does not adequately take into account the constraint
known as ``Hypermedia as the Engine of Application State'' (commonly
abbreviated HATEOAS) from the REST architectural style, see
\cite{fielding}~Chapter~5.
